---
title: "Exploring the Postsynaptic Density with PSDExplorer"
author: "Ana Ciur"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Exploring the Postsynaptic Density with PSDExplorer}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(PSDExplorer)
```
  
### **1. Introduction**
The **PSDExplorer** package provides a reproducible interface to explore
protein–protein interaction networks within the **postsynaptic density (PSD)**.
It integrates an embedded Python engine (via `reticulate`) to iteratively build
and visualize layered PSD networks starting from seed scaffold proteins.

In this vignette, you’ll learn how to:
1. Load PSD data from the included example file
2. Generate a multi-layer PSD network
3. Visualize the resulting HTML graph
4. Perform simple network inspection in R

---

  ### **2. Quick Start**

```{r}
# Load example data (placeholder)
psd_data <- loadPSD()
head(psd_data)

{r eval=FALSE}
# Run the embedded Python engine (skipped during vignette build)
output_html <- runPythonPSD(layers = 3, min_int = 2)
browseURL(output_html)

# Open the generated network
browseURL(output_html)

## Detect clusters and summarize
# clusters <- detectClusters(psd_data)
# summaryStats(clusters)
#(not yet implemented)

## Workflow Summary
cat("
  loadPSD() – Load and validate input data⃣
  runPythonPSD() – Build the multi-layer network
  detectClusters() – Identify modules
  runGOenrichment() – Biological interpretation
  plotPSDnetwork() – Interactive visualization
")

## Reproducibility
sessionInfo()
```
